\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-15 phd-cs-us.tex
Updates from Overleaf
updates

\newcommand{\mycomment}[3][\color{blue}]{{#1{{#2}: {#3}}}}
\newcommand{\tvn}[1]{\mycomment{TVN}{#1}}{}
\newcommand{\didi}[1]{\mycomment{Didier}{#1}}{}
\newcommand{\tl}[1]{\mycomment{ThanhLe}{#1}}{}
\newcommand{\red}[1]{{\color{red}{#1}}}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\title{\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students}}
%\date{\today}
\author{\small \href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen} (\href{mailto:tvn@gmu.edu}{tvn@gmu.edu})\\
 \href{https://cs.gmu.edu}{George Mason University}}

@@

\begin{commentbox}[Vu] 
We usually decide that a PhD candidate is either (i) admit with funding (TA or RA) or (ii) rejected. In other words, in most cases, we either
admit you with full funding, or we don't. In some rare cases, we admit
without funding because you have funding on your own (e.g.,
supported by your government or having external grants). We also justify
our decision with a summary about your application, where we list
strengths (e.g., well-known school) and weaknesses (e.g., weak
LORs). 
\end{commentbox}

>>>>

\newcommand{\mycomment}[3][\color{blue}]{{#1{{#2}: {#3}}}}
\newcommand{\tvn}[1]{\mycomment{TVN}{#1}}{}
\newcommand{\didi}[1]{\mycomment{Didier}{#1}}{}
\newcommand{\tl}[1]{\mycomment{ThanhLe}{#1}}{}
\newcommand{\red}[1]{{\color{red}{#1}}}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\title{\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students}}
%\date{\today}
\author{\small \href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen} (\href{mailto:tvn@gmu.edu}{tvn@gmu.edu})}

@@

\begin{commentbox}[Vu] 
We usually decide that a full-time PhD candidate is either (i) admit with funding (TA or RA) or (ii) rejected. In other words, in most cases, we either
admit you with full funding, or we don't. In some rare cases, we admit
without funding because you have funding on your own (e.g.,
supported by your government or having external grants). We also justify
our decision with a summary about your application, where we list
strengths (e.g., well-known school) and weaknesses (e.g., weak
LORs). 
\end{commentbox}
